Efficient Parallelization of Sparse Representation for Face Recognition

### 2010-10-20 paper/main.tex
Added missing style files
Writing the outline...

>>>>

\section{Characteristics of the ALM Algorithm}
Describe the two variants of the ALM algorithm
Show Pseudocode for one variant
\subsection{Computational Complexity}

\section{Efficient Implementation on the CPU}
% With a reshuffling of the order of operations and a change of the termination
% condition, the inner loop takes the form of two matrix-vector multiplications
% and a sequence of vector-vector operations.
\subsection{CPU Hardware Parallelism}
High-level discussion of CPU parallelism, i.e.
thread-level, vector-level, cache size, cache locality
\subsection{Tuning the GEMV operation}
When matrix-vector operations are called sequentially on the same data,
the operation can be blocked so that each thread operates on the same block of data for each operation.

For Single threaded MKL sgemv, Code took          0.0335823 msec per instance to run!

For Automatic multi-threaded MKL sgemv, Code took 0.008179 msec per instance to run!

For Manually multi-threaded MKL sgemv, Code took  0.0061276 msec per instance to run!

\subsection{Tuning the Soft-Thresholding Operator}
...Make sure there are no branches

...Make sure there are no function calls

...Make sure the loop gets automatically vectorized

...Block the computation into work for different cpu cores

\section{Efficient Implementation on the CPU}
\subsection{GPU Hardware Parallelism}
High-level description of GPU parallelism, i.e.

cuda cores, SIMD width, scheduling restrictions, bandwidth

\subsection{Solving multiple L1 minimizations in parallel}
This section is about Drew's kernels for solving multiple L1 minimizations in parllel

How to efficiently perform an L1 minimization on a single core, quote performance on a large batch.

How to solve multiple instances in smaller batches without losing concurrency, using CUDA streams.

...Mention effect of compiler verion on streams implementation
